Validate Bayes-Nash Equilibrium Model in First-Price Reverse Auctions \footnote{ All code and data are located at \url{https://github.com/QuRyu/CDOT/} }

### 2021-06-16 paper/paper.tex
rename folder

\title{% 
    Validate Nash-Equilibrium Equilibrium Model 
    in First-Price Reverse Auctions}

\author{Qingbo Liu\\[0.5cm]{\small Advisor: Timothy P. Hubbard}}

@@

\begin{abstract}
    This paper tests the predictive power of Bayes-Nash equilibrium model in 
    first-price procurement auctions through validation set approach. It 
    first trains the model on a subset of data using the Guerre-Perrigne-Vuong method 
    and then generates predictions on validation set using inversion method. 
    The generated predictions are compared to the actual data from validation set.
    This paper's result suggests that Bayes-Nash equilibrium model does not 
    yield accurate predictions but the answer might be more nuanced due to 
    flaws in the paper's approach. 
\end{abstract}

@@

Figure \ref{fig:actualVsimulation} plots test data against simulated bids. 
A wide difference between simulation and test data is observed here. 
This difference, however, is not unexpected for two reasons: 
(1) the validation data, which contains an auction with 16 bidders, does not conform 
to the bid distribution depicted in Figure \ref{fig:BidFrequency}, and 
(2) I am comparing most likely bids predicted by the estimated cost distribution 
to a particular auction. Therefore, the difference here does not suggest the 
inaccuracy of the estimated cost distribution or the equilibrium model. 
Instead, this exercise suggests that a larger test dataset is needed 
to deliver more informative results and raises the need for a better 
way to compare simulation data to validation data.

@@

\pagebreak
\begin{appendices}
    Please refer to \url{https://github.com/QuRyu/CDOT/tree/main/Extensions} for code.
\end{appendices}

>>>>

\title{% 
    Validate Bayes-Nash Equilibrium Model 
    in First-Price Reverse Auctions 
    \footnote{ All code and data are located at
    \url{https://github.com/QuRyu/CDOT/} }}

\author{Qingbo Liu\\[0.5cm]{\small Advisor: Timothy P. Hubbard}}
\date{\vspace{-5ex}}

@@

\begin{abstract}
    This paper tests the predictive power of Bayes-Nash equilibrium model in 
    first-price procurement auctions through validation set approach. It 
    estimates the equilibrium model on a subset of data using the 
    Guerre-Perrigne-Vuong method 
    and then generates predictions on validation set using inversion method. 
    The generated predictions are compared to validation set.
    The result suggests that Bayes-Nash equilibrium model might not 
    yield accurate predictions but the answer might be more nuanced due to 
    flaws in the paper's approach. 
\end{abstract}

@@

Figure \ref{fig:actualVsimulation} plots test data against simulated bids. 
A wide difference between simulation and test data is observed here. 
This difference, however, is not unexpected. 
The validation data, which contains an auction with 16 bidders, does not conform 
to the bid distribution depicted in Figure \ref{fig:BidFrequency}. 
The calibrated model has only learnt information from the training data and 
so can only make predictions from what it already knows. This might imply that 
equilibrium model adopted in this paper is not robust to new data. 
To derive more meaningful comparisons, I need to augment the size of validation set.
For example, 80\% of available data should be used for training and 20\% of 
data for validation. 
However, due to time limit that this term paper imposes, I have not proceeded 
further.

@@
